Ice sheet mass flows

### 2025-06-23 sankey.tex
Use 'mass loss (gain)' not 'drawdown/retreat (buildup/expansion)'

    \ifthenelse{\Q{vMG} < \Q{vML}} { % mass loss
      \sankeynode{name=ML, quantity=\Q{vML},
        at={[yshift=6mm]RF.north}, anchor=right, angle=-45}
      \node[font=\tiny, anchor=east]
      at ([xshift=-3mm,yshift=2mm]ML.west) {Drawdown or retreat: \qq{ML}};

@@

      \sankeystart[red]{ML}
      \sankeyadvance[red]{ML}{5mm}
      \sankeyoutin[red-to-ice]{ML}{MLi}
    }{ % mass gain
      \sankeynode{name=MGa, quantity=\qq{MG}, angle=-35,
        at={[xshift=5mm,yshift=-3mm]MG.right}, anchor=right}
      \node[font=\tiny, anchor=east]
        at ([yshift=0mm,xshift=0mm]MGa.right) {Build-up or expansion: \qq{MGa}};
      \sankeyoutin[ice-to-black]{MG}{MGa}; \sankeyadvance[black]{MGa}{3mm}
      \sankeyend[black]{MGa}
      \sankeynode{name=FRONTADVi, quantity=\Q{vFRONTADV},
        at={[xshift=-15mm,yshift=8mm]RFZi.right}, anchor=left, angle=-45}
    }

>>>>

    \ifthenelse{\Q{vMG} < \Q{vML}} { % mass loss
      \sankeynode{name=ML, quantity=\Q{vML},
        at={[yshift=6mm]RF.north}, anchor=right, angle=-45}
      \node[font=\tiny, anchor=east]
      at ([xshift=-3mm,yshift=2mm]ML.west) {Mass loss: \qq{ML}};

@@

      \sankeystart[red]{ML}
      \sankeyadvance[red]{ML}{5mm}
      \sankeyoutin[red-to-ice]{ML}{MLi}
    }{ % mass gain
      \sankeynode{name=MGa, quantity=\qq{MG}, angle=-35,
        at={[xshift=5mm,yshift=-3mm]MG.right}, anchor=right}
      \node[font=\tiny, anchor=east]
        at ([yshift=0mm,xshift=0mm]MGa.right) {Mass gain: \qq{MGa}};
      \sankeyoutin[ice-to-black]{MG}{MGa}; \sankeyadvance[black]{MGa}{3mm}
      \sankeyend[black]{MGa}
      \sankeynode{name=FRONTADVi, quantity=\Q{vFRONTADV},
        at={[xshift=-15mm,yshift=8mm]RFZi.right}, anchor=left, angle=-45}
    }
